\documentclass{standard}
\title{The Watsons Go To Birmingham}
\author{Christopher Paul Curtis}
\date{}
\begin{document}
\maketitle
\newpage


\section{And You Wonder Why We Get Called the Weird Watsons}
It was one of those super-duper-cold Saturdays. One of those days that when you breathed out your breath kind of hung frozen in the air like a hunk of smoke and you could walk along and look exactly like a train blowing out big, fat, white puffs of smoke.\\

It was so cold that if you were stupid enough to go outside your eyes would automatically blink a thousand times all by themselves, probably so the juice inside of them wouldn’t freeze up. It was so cold that if you spit, the slob would be an ice cube before it hit the ground. It was about a zillion degrees below zero.\\

It was even cold inside our house. We put sweaters and hats and scarves and three pairs of socks on and still were cold.The thermostat was turned all the way up and the furnace was banging and sounding like it was about to blow up but it still felt like Jack Frost had moved in with us.\\

All of my family sat real close together on the couch under a blan- ket. Dad said this would generate a little heat but he didn’t have to tell us this, it seemed like the cold automatically made us want to get together and huddle up. My little sister, Joetta, sat in the middle and all you could see were her eyes because she had a scarf wrapped around her head. I was next to her, and on the outside was my mother.\\

Momma was the only one who wasn’t born in Flint so the cold was coldest to her. All you could see were her eyes too, and they were ￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼shooting bad looks at Dad. She always blamed him for bringing her all the way from Alabama to Michigan, a state she called a giant icebox. Dad was bundled up on the other side of Joey, trying to look at any- thing but Momma. Next to Dad, sitting with a little space between them, was my older brother, Byron.\\

Byron had just turned thirteen so he was officially a teenage juvenile delinquent and didn’t think it was “cool” to touch anybody or let anyone touch him, even if it meant he froze to death. Byron had tucked the blanket between him and Dad down into the cushion of the couch to make sure he couldn’t be touched.\\

Dad turned on the TV to try to make us forget how cold we were but all that did was get him in trouble.There was a special news report on Channel 12 telling about how bad the weather was and Dad groaned when the guy said, “If you think it’s cold now, wait until tonight, the temperature is expected to drop into recordlow territory, possibly reaching the negative twenties! In fact, we won’t be seeing anything above zero for the next four to five days!” He was smiling when he said this but none of the Watson family thought it was funny. We all looked over at Dad. He just shook his head and pulled the blanket over his eyes.\\

Then the guy on TV said, “Here’s a little something we can use to brighten our spirits and give us some hope for the future: The temperature in Atlanta, Georgia, is forecast to reach...” Dad coughed real loud and jumped off the couch to turn the TV off but we all heard the weatherman say, “...the mid-seventies!” The guy might as well have tied Dad to a tree and said, “Ready, aim, fire!”\\

Momma said.“That’s a hundred and fifty miles from home!” “Wilona...,” Dad said.\\

“I knew it,”Momma said.“I knew I should have listened to Moses Henderson!”\\

“Who?” I asked.\\

Dad said,“Oh Lord, not that sorry story.You’ve got to let me tell about what happened with him.”\\

Momma said, “There’s not a whole lot to tell, just a story about a young girl who made a bad choice. But if you do tell it, make sure you get all the facts right.”\\

We all huddled as close as we could get because we knew Dad was ￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼going to try to make us forget about being cold by cutting up. Me and Joey started smiling right away, and Byron tried to look cool and bored.
“Kids,” Dad said, “I almost wasn’t your father.You guys came real close to having a clown for a daddy named Hambone Henderson. . . .” “Daniel Watson, you stop right there.You’re the one who started that ‘Hambone’ nonsense. Before you started that everyone called him his Christian name, Moses. And he was a respectable boy too, he was-
n’t a clown at all.”
“But the name stuck, didn’t it? Hambone Henderson. Me and your
granddaddy called him that because the boy had a head shaped just like a hambone, had more knots and bumps on his head than a dinosaur. So as you guys sit here giving me these dirty looks because it’s a little chilly outside ask yourselves if you’d rather be a little cool or go through life being known as the Hambonettes.”
Me and Joey cracked up, Byron kind of chuckled and Momma put her hand over her mouth. She did this whenever she was going to give a smile because she had a great big gap between her front teeth. If Momma thought something was funny, first you’d see her trying to keep her lips together to hide the gap, then, if the smile got to be too strong, you’d see the gap for a hot second before Momma’s hand would come up to cover it, then she’d crack up too.
Laughing only encouraged Dad to cut up more, so when he saw the whole family thinking he was funny he really started putting on a show.
He stood in front of the TV. “Yup, Hambone Henderson proposed to your mother around the same time I did. Fought dirty too, told your momma a pack of lies about me and when she didn’t believe them he told her a pack of lies about Flint.”
Dad started talking Southern-style, imitating this Hambone guy. “Wilona, I heard tell about the weather up that far north in Flint, Mitch-again, heard it’s colder than inside a icebox. Seen a movie about it, think it was made in Flint. Movie called Nanook of the North.Yup, do believe for sure it was made in Flint. Uh-huh, Flint, Mitch-again.
“Folks there live in these things called igloos. According to what I seen in this here movie most the folks in Flint is Chinese. Don’t believe I seen nan one colored person in the whole dang city. You a
￼3
￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼’Bama gal, don’t believe you’d be too happy living in no igloo. Ain’t got nothing against ’em, but don’t believe you’d be too happy living ’mongst a whole slew of Chinese folks. Don’t believe you’d like the food. Only thing them Chinese folks in that movie et was whales and seals. Don’t believe you’d like no whale meat. Don’t taste a lick like chicken. Don’t taste like pork at all.”
Momma pulled her hand away from her mouth. “Daniel Watson, you are one lying man! Only thing you said that was true was that being in Flint is like living in a igloo. I knew I should have listened to Moses. Maybe these babies mighta been born with lumpy heads but at least they’da had warm lumpy heads!
“You know Birmingham is a good place, and I don’t mean just the weather either.The life is slower, the people are friendlier—”
“Oh yeah,” Dad interrupted,“they’re a laugh a minute down there. Let’s see, where was that ‘Coloreds Only’ bathroom downtown?”
“Daniel, you know what I mean, things aren’t perfect but people are more honest about the way they feel”—she took her mean eyes off Dad and put them on Byron—“and folks there do know how to respect their parents.”
Byron rolled his eyes like he didn’t care. All he did was tuck the blanket farther into the couch’s cushion.
Dad didn’t like the direction the conversation was going so he called the landlord for the hundredth time.The phone was still busy.
“That snake in the grass has got his phone off the hook. Well, it’s going to be too cold to stay here tonight, let me call Cydney. She just had that new furnace put in, maybe we can spend the night there.” Aunt Cydney was kind of mean but her house was always warm so we kept our fingers crossed that she was home.
Everyone, even Byron, cheered when Dad got Aunt Cydney and she told us to hurry over before we froze to death.
Dad went out to try and get the Brown Bomber started.That was what we called our car. It was a 1948 Plymouth that was dull brown and real big, Byron said it was turd brown. Uncle Bud gave it to Dad when it was thirteen years old and we’d had it for two years. Me and Dad took real good care of it but some of the time it didn’t like to start up in the winter.
After five minutes Dad came back in huffing and puffing and slap-
￼4
￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼ping his arms across his chest.
“Well, it was touch and go for a while, but the Great Brown One
pulled through again!” Everyone cheered, but me and Byron quit cheering and started frowning right away. By the way Dad smiled at us we knew what was coming next. Dad pulled two ice scrapers out of his pocket and said, “O.K., boys, let’s get out there and knock those windows out.”
We moaned and groaned and put some more coats on and went outside to scrape the car’s windows. I could tell by the way he was pouting that Byron was going to try and get out of doing his share of the work.
“I’m not going to do your part, Byron, you’d better do it and I’m not playing either.”
“Shut up, punk.”
I went over to the Brown Bomber’s passenger side and started hack- ing away at the scab of ice that was all over the windows. I finished Momma’s window and took a break. Scraping ice off of windows when it’s that cold can kill you!
I didn’t hear any sound coming from the other side of the car so I yelled out, “I’m serious, Byron, I’m not doing that side too, and I’m only going to do half the windshield, I don’t care what you do to me.” The windshield on the Bomber wasn’t like the new 1963 cars, it had a big bar running down the middle of it, dividing it in half.
“Shut your stupid mouth, I got something more important to do right now.”
I peeked around the back of the car to see what By was up to.The only thing he’d scraped off was the outside mirror and he was bend- ing down to look at himself in it. He saw me and said, “You know what, square? I must be adopted, there just ain’t no way two folks as ugly as your momma and daddy coulda give birth to someone as sharp as me!”
He was running his hands over his head like he was brushing his hair.
I said, “Forget you,” and went back over to the other side of the car to finish the back window. I had half of the ice off when I had to stop again and catch my breath. I heard Byron mumble my name.
I said, “You think I’m stupid? It’s not going to work this time.” He
￼5
￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼mumbled my name again. It sounded like his mouth was full of some- thing. I knew this was a trick, I knew this was going to be How to Survive a Blizzard, Part Two.
How to Survive a Blizzard, Part One had been last night when I was outside playing in the snow and Byron and his running buddy, Buphead, came walking by. Buphead has officially been a juvenile delinquent even longer than Byron.
“Say, kid,” By had said,“you wanna learn somethin’ that might save your stupid life one day?”
I should have known better, but I was bored and I think maybe the cold weather was making my brain slow, so I said, “What’s that?”
“We gonna teach you how to survive a blizzard.”
“How?”
Byron put his hands in front of his face and said,“This is the most
important thing to remember, O.K.?” “Why?”
“Well, first we gotta show you what it feels like to be trapped in a blizzard.You ready?” He whispered something to Buphead and they both laughed.
“I’m ready.”
I should have known that the only reason Buphead and By would want to play with me was to do something mean.
“O.K.,” By said,“first thing you gotta worry about is high winds.”
Byron and Buphead each grabbed one of my arms and one of my legs and swung me between them going, “Wooo, blizzard warnings! Blizzard warnings! Wooo! Take cover!”
Buphead counted to three and on the third swing they let me go in the air. I landed headfirst in a snowbank.
But that was O.K. because I had on three coats, two sweaters, a T- shirt, three pairs of pants and four socks along with a scarf, a hat and a hood.These guys couldn’t have hurt me if they’d thrown me off the Empire State Building!
After I climbed out of the snowbank they started laughing and so did I.
“Cool, Baby Bruh,” By said,“you passed that part of the test with a B-plus, what you think, Buphead?”
Buphead said, “Yeah, I’d give the little punk a A.”
￼6
￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼They whispered some more and started laughing again.
“O.K.,” By said,“second thing you gotta learn is how to keep your balance in a high wind.You gotta be good at this so you don’t get blowed into no polar bear dens.”
They put me in between them and started making me spin round and round, it seemed like they spun me for about half an hour.When slob started flying out of my mouth they let me stop and I wobbled around for a while before they pushed me back in the same snowbank.
When everything stopped going in circles I got up and we all laughed again.
They whispered some more and then By said, “What you think, Buphead? He kept his balance a good long time, I’m gonna give him a A-minus.”
“I ain’t as hard a grader as you, I’ma give the little punk a double A-minus.”
“O.K., Kenny, now the last part of Surviving a Blizzard, you ready?” “Yup!”
“You passed the wind test and did real good on the balance test but
now we gotta see if you ready to graduate.You remember what we told you was the most important part about survivin’?”
“Yup!”
“O.K., here we go. Buphead, tell him ’bout the final exam.” Buphead turned me around to look at him, putting my back to
Byron. “O.K., square,” he started, “I wanna make sure you ready for this one, you done so good so far I wanna make sure you don’t blow it at graduation time.You think you ready?”
I nodded, getting ready to be thrown in the snowbank real hard this time. I made up my mind I wasn’t going to cry or anything, I made up my mind that no matter how hard they threw me in that snow I was going to get up laughing.
“O.K.,” Buphead said, “everything’s cool, you ’member what your brother said about puttin’ your hands up?”
“Like this?” I covered my face with my gloves.
“Yeah, that’s it!” Buphead looked over my shoulder at Byron and then said, “Wooo! High winds, blowing snow! Wooo! Look out! Blizzard a-comin’! Death around the corner! Look out!”
Byron mumbled my name and I turned around to see why his voice
￼7
￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼sounded so funny.As soon as I looked at him Byron blasted me in the face with a mouthful of snow.
Man! It was hard to believe how much stuff By could put in his mouth! Him and Buphead just about died laughing as I stood there with snow and spit and ice dripping off of my face.
Byron caught his breath and said, “Aww, man, you flunked! You done so good, then you go and flunk the Blowin’ Snow section of How to Survive a Blizzard, you forgot to put your hands up! What you say, Buphead, F?”
“Yeah, double F-minus!”
It was a good thing my face was numb from the cold already or I might have froze to death. I was too embarrassed about getting tricked to tell on them so I went in the house and watched TV.
So as me and By scraped the ice off the Brown Bomber I wasn’t going to get fooled again. I kept on chopping ice off the back win- dow and ignored By’s mumbling voice.
The next time I took a little rest Byron was still calling my name but sounding like he had something in his mouth. He was saying, “Keh-ee! Keh-ee! Hel’ . . . hel’ . . . !”When he started banging on the door of the car I went to take a peek at what was going on.
By was leaned over the outside mirror, looking at something in it real close. Big puffs of steam were coming out of the side of the mirror.
I picked up a big, hard chunk of ice to get ready for Byron’s trick.
“Keh-ee! Keh-ee! Hel’ me! Hel’ me! Go geh Momma! Go geh Mom-ma! Huwwy uh!”
“I’m not playing, Byron! I’m not that stupid! You’d better start doing your side of the car or I’ll tear you up with this iceball.”
He banged his hand against the car harder and started stomping his feet. “Oh, please, Keh-ee! Hel’ me, go geh Mom-ma!”
I raised the ice chunk over my head.“I’m not playing,By,you bet- ter get busy or I’m telling Dad.”
I moved closer and when I got right next to him I could see boogers running out of his nose and tears running down his cheeks. These weren’t tears from the cold either, these were big juicy crybaby tears! I dropped my ice chunk.
“By! What’s wrong?”
“Hel’ me! Keh-ee! Go geh hel’!”
￼8
￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼I moved closer. I couldn’t believe my eyes! Byron’s mouth was frozen on the mirror! He was as stuck as a fly on flypaper!
I could have done a lot of stuff to him. If it had been me with my lips stuck on something like this he’d have tortured me for a couple of days before he got help. Not me, though, I nearly broke my neck try- ing to get into the house to rescue Byron.
As soon as I ran through the front door Momma, Dad and Joey all yelled,“Close that door!”
“Momma, quick! It’s By! He’s froze up outside!”
No one seemed too impressed.
I screamed,“Really! He’s froze to the car! Help! He’s crying!” That shook them up.You could cut Byron’s head off and he prob-
ably wouldn’t cry.
“Kenneth Bernard Watson, what on earth are you talking about?” “Momma, please hurry up!”
Momma, Dad and Joey threw on some extra coats and followed me
to the Brown Bomber.
The fly was still stuck and buzzing. “Oh, Mom-ma! Hel’ me! Geh
me offa ’ere!”
“Oh my Lord!” Momma screamed, and I thought she was going to
do one of those movie-style faints, she even put her hand over her forehead and staggered back a little bit.
Joey, of course, started crying right along with Byron.
Dad was doing his best not to explode laughing. Big puffs of smoke were coming out of his nose and mouth as he tried to squeeze his laughs down. Finally he put his head on his arms and leaned against the car’s hood and howled.
“Byron,” Momma said, gently wiping tears off his cheeks with the end of her scarf,“it’s O.K., sweetheart, how’d this happen?” She sound- ed like she was going to be crying in a minute herself.
Dad raised his head and said, “Why are you asking how it hap- pened? Can’t you tell,Wilona?This little knucklehead was kissing his reflection in the mirror and got his lips stuck!” Dad took a real deep breath.“Is your tongue stuck too?”
“No! Quit teasin’, Da-ee! Hel’! Hel’!”
“Well, at least the boy hadn’t gotten too passionate with himself!” Dad thought that was hilarious and put his head back on his arms.
￼9
￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼Momma didn’t see anything funny. “Daniel Watson! What are we gonna do? What do y’all do when this happens up he-uh?” Momma started talking Southernstyle when she got worried. Instead of saying “here” she said “he-uh” and instead of saying “you all” she said “y’all.”
Dad stopped laughing long enough to say, “Wilona, I’ve lived in Flint all my life, thirty-five years, and I swear this is the first time I’ve ever seen anyone with their lips frozen to a mirror. Honey, I don’t know what to do, wait till he thaws out?”
“Pull him off, Dad,” I suggested. Byron went nuts! He started bang- ing his hands on the Brown Bomber’s doors again and mumbling, “No! No! Mom-ma, doe leh him!”
Joey blubbered out,“This is just like that horrible story Kenny read me about that guy Nar-sissy who stared at himself so long he forgot to eat and starved to death. Mommy, please save him!” She went over and hugged her arms around stupid Byron’s waist.
Momma asked Dad, “What about hot water? Couldn’t we pour enough hot water on the mirror so it would warm up and he could get off?” She kept wiping tears off By’s cheeks and said, “Don’t you worry, Baby, we gonna get you off of this.” But her voice was so shaky and Southern that I wondered if we’d be driving around in the sum- mer with a skeleton dangling from the outside mirror by its lips.
Dad said,“I don’t know, pouring water on him might be the worst thing to do, but it might be our only chance. Why don’t you go get some hot tap water and I’ll stay to wipe his cheeks.”
Joey told By, “Don’t worry, we’ll come right back.” She stood on her tiptoes and gave By a kiss, then she and Momma ran inside. Dad cracked up all over again.
“Well, lover boy, I guess this means no one can call you Hot Lips, can they?”
Dad was killing himself.“Or the Last of the Red Hot Lovers either, huh?” He tugged on Byron’s ear a little, pulling his face back.
By went nuts again. “Doe do dat! Mom-ma! Momma, hel’! Keh- ee, go geh Mom-ma! Huwwy!”
“Hmm, I guess that’s not going to work, is it?”
Every time he wiped away the tears and the little mustache of boogers on Byron’s lip Dad couldn’t help laughing, until a little river of tears was coming out of his eyes too.
￼10
￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼Dad tried to straighten his face out when Momma and Joey came running back with a steaming glass of hot water, but the tears were still running down his cheeks.
Momma tried to pour water on the mirror but her hands were shaking so much, she was splashing it all over the place. Dad tried too, but he couldn’t look at Byron without laughing and shaking.
That meant I had to do it.
I knew that if my lips were frozen on something and everybody was shaking too much to pour water on them except for Byron he’d do some real cruel stuff to me. He probably would have “accidentally” splashed my eyes until they were frozen open or put water in my ears until I couldn’t hear anything, but not me. I gently poured a little stream of water over the mirror.
Dad was right! This was the worst thing we could do! The water made a cracking sound and froze solid as soon as it touched the mir- ror and By’s lips!
Maybe By’s mouth was frozen but his hands sure weren’t and he popped me right in the forehead. Hard! I hate to say it but I started crying too.
It’s no wonder the neighbors called us the Weird Watsons behind our backs.There we were, all five of us standing around a car with the temperature about a million degrees below zero and each and every one of us crying!
“ ’top! ’top!” By yelled.
“Daniel Watson, what’re we gonna do?” Momma went nuts. “You gotta get this boy to the hospital! My baby is gonna die!”
Dad tried to look serious real quick.
“Wilona, how far do you think I’d get driving down the street with this little clown attached to the mirror? What am I supposed to do, have him run beside the car all the way down to the emergency room?”
Momma looked real close at By’s mouth, closed her eyes for a sec- ond like she was praying and finally said, “Daniel, you get in there and call the hospital and see what they say we should do. Joey and Kenny, go with your daddy.”
Dad and Joey went crying into the house. I stayed by the Brown Bomber. I figured Momma was clearing everybody out for something.
￼11
￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼Byron did too and looked at Momma in a real nervous way. Momma put her scarf around Byron’s face and said, “Sweetheart, you know we gotta do something. I’ma try to warm your face up a
little. Just relax.”
“O.K., Mom-ma.”
“You know I love you and wouldn’t do anything to hurt you,
right?” If Momma was trying to make Byron relax she wasn’t doing a real good job at it. All this talk about love and not getting hurt was making him real nervous.
“Wah are you gonna do? Huh? Doe hur’ me! Keh-ee, hel’!”
Momma moved the scarf away and put one hand on Byron’s chin and the other one on his forehead.
“No! Hel’! Hel’ me, Keh-ee!”
Momma gave Byron’s head a good hard snatch and my eyes auto- matically shut and my hands automatically flew up to cover my ears and my mouth automatically flew open and screamed out, “Yeeeowwww!”
I didn’t see it, but I bet Byron’s lips stretched a mile before they finally let go of that mirror. I bet his lips looked like a giant rubber band before they snapped away from that glass!
I didn’t hear it, but I bet Byron’s lips made a sound like a giant piece of paper being ripped in half!
When I opened my eyes Byron was running to the house with his hands over his mouth and Momma following right behind him. I ran over to the mirror to see how much of Byron’s mouth was still stuck there.
The dirty dogs let Byron get away with not doing his share of the windows and I had to do the whole car myself.When we were final- ly going to Aunt Cydney’s house I decided to pay Byron back for punching me in the forehead and getting out of doing his part of the window scraping. Joey was sitting between us so I felt kind of safe. I said to her, loud, “Joetta, guess what. I’m thinking about writing my own comic book.”
“What about?”
“Well, it’s going to be about this real mean criminal who has a ter- rible accident that turns him into a superhero.”
Joey knew I was going to tease Byron so she sat there looking like I should be careful what I said. Finally I asked her, “Do you want to
￼12
￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼￼
know what I’m going to call this new superhero?” “What?”
“I’m going to call him the Lipless Wonder. All he does is beat up superheroes smaller than him and the only thing he’s afraid of is a cold mirror!”
All the Weird Watsons except Byron cracked up. Momma’s hand even covered her mouth. I was the only one who saw Byron flip me a dirty finger sign and try to whisper without smearing all theVaseline Momma had put on his lips, “You wait, I’m gonna kick your little behind.” Then he made his eyes go crossed, which was his favorite way of teasing me, but I didn’t care, I knew who had won this time!
\end{document}
