\documentclass{hw}

\begin{document}
\noindent\textbf{Steven Rosendahl}\\
\noindent\textbf{CPSC 125 Lab I}\\
\section*{Careers in CS and CE}
\begin{enumerate}
\item What are five professions within the fields of computer science or computer engineering? Provide a short job description for each of them. What is the income potential for these types of jobs? Give numbers. How do they compare to other professions? Give a few examples. What are the employment projections for the next 5 to 10 years for these five professions?
\begin{enumerate}
\item Cybersecurity - Writing code to protect people on the web. The pay is an average of \$100,000 a year. The job market for Cybersecurity is very understaffed and will continue growing in the next 5-10 years.
\item Mobile Development - Designing and building applications for mobile devices (tables, phones, wearables, etc...). The pay is an average of \$72,000 annually. Nearly every website I visited suggested that the job market would continue growing for this job.
\item Web Developer - Building webpages and web-apps on the internet and sometimes working on back-end code. The average pay is about \$55,000. The demand for web developers is projected to grow 27\% in the next several years.
\item Developer Operations Specialist - A devops is someone who suffers at the hands of the developers. A devops is in charge of managing systems and teams when developing software. The average salary for a devops specialist is \$100,000 a year. The field is projected to grow, as well as provide room for people to move into management. This is one of the more higher-paying jobs that I looked up.
\item Database Manager - A database manager is someone who manages databases, usually for a large company. The average pay is around \$70,000 per year. The market is projected to grow around 11\% in the next few years.
\end{enumerate}
\item Which CS/CE specialization does your team consider the most interesting one? Why?
\begin{quote}
I think that Mobile Development is one of the more interesting fields, since mobile devices are becoming more and more powerful and widespread every day. The market has a lot of promise and doesn't seem to be in high demand.
\end{quote}
\item What are some other interesting facts about CS/CE careers that you came across during your research?
\begin{quote}
I searched for CE jobs a few times and most of the CE jobs were programming based, which is not something that I expected. Typically, I think of CE people as designing circuitry and working more with hardware.
\end{quote}
\end{enumerate}

\section*{Interviewing Another Student}

I interviewed Matt McCarthy for this part of the assignment.
\begin{enumerate}
\item What is your major and why did you choose it?
\begin{quote}
Computer Science, since CNU doesn't have a math masters
\end{quote}
\item What do you like/dislike about your major?
\begin{quote}
I like that it gives me an excuse to do math/focus on the theoretical side of math. I don't like having to run simulations and experiments.
\end{quote}
\item What was your favorite class you took?
\begin{quote}
Parallel Processing (a 600 level class)
\end{quote}
\item What's your favorite proof? Your least favorite proof?
\begin{quote}
Favorite: Fundamental Homomorphism Proof. Least Favorite: Anything that involves heavy calculation.
\end{quote}
\item Do you have any advice for students in the major?
\begin{quote}
Don't be afraid of math.
\end{quote}
\end{enumerate}
\end{document}
